Article Title

### 2018-02-28 doc/letter_editor.tex
started edits for plos one

\begin{document}
\begin{letter}{Editor \\ \textit{Biological Journal of the Linnean Society}}
  \opening{Dear Editor,}

  Please find enclosed the manuscript entitled ``Ensemble approaches for estimating congruence between species delimitation and morphological variation: comparing taxonomic hypotheses for the Pacific Pond Turtle (\textit{Emys marmorata})'' which we are submitting for consideration for the \textit{Biological Journal of the Linnean Society}. This manuscript is authored by myself (Peter D Smits), Kenneth D Angielczyk, James F Parham, and Bryan L Stuart. We believe our analysis and results are of interest to the community as we present a non-standard approach for evaluating the intensity of cryptic diversity and the efficacy of different classification schemes.

>>>>

\begin{document}
\begin{letter}{Editor \\ \textit{PeerJ}}
  \opening{Dear Editor,}

  Please find enclosed the manuscript entitled ``Ensemble approaches for estimating congruence between species delimitation and morphological variation: comparing taxonomic hypotheses for the Pacific Pond Turtle (\textit{Emys marmorata})'' which we are submitting for consideration for the \textit{PeerJ}. This manuscript is authored by myself (Peter D Smits), Kenneth D Angielczyk, James F Parham, and Bryan L Stuart. We believe our analysis and results are of interest to the community as we present a non-standard approach for evaluating the intensity of cryptic diversity and the efficacy of different classification schemes.

### 2018-02-28 doc/turtles_peerj.tex
started edits for plos one

\author[1]{Peter D Smits}%\thanks{peterdavidsmits@gmail.com}}
\author[2]{Kenneth D Angielczyk}%\thanks{kangielczyk@fieldmuseum.org}}
\author[3]{James F Parham}%\thanks{jparham@fullerton.edu}}
\author[4]{Bryan L Stuart}%\thanks{bryan.stuart@naturalsciences.org}}
\affil[1]{Department of Integrative Biology, University of California -- Berkeley}
\affil[2]{Integrative Research Center, Field Museum of Natural History}
\affil[3]{John D. Cooper Archaeological and Paleontological Center, Department of Geological Sciences, California State University, Fullerton}
\affil[4]{Section of Research and Collections, North Carolina Museum of Natural Sciences}
\corrauthor[1]{Peter D Smits}{psmits@berkeley.edu}

@@

\subsection*{Is there more than one species of Western Pond Turtle?}

@@

\bibliography{turtle,packages}

>>>>

\author[1]{Peter D Smits}%\thanks{peterdavidsmits@gmail.com}}
\author[2]{Kenneth D Angielczyk}%\thanks{kangielczyk@fieldmuseum.org}}
\author[3]{Bryan L Stuart}%\thanks{bryan.stuart@naturalsciences.org}}
\author[4]{James F Parham}%\thanks{jparham@fullerton.edu}}
\affil[1]{Department of Integrative Biology, University of California -- Berkeley}
\affil[2]{Integrative Research Center, Field Museum of Natural History}
\affil[3]{Section of Research and Collections, North Carolina Museum of Natural Sciences}
\affil[4]{John D. Cooper Archaeological and Paleontological Center, Department of Geological Sciences, California State University, Fullerton}
\corrauthor[1]{Peter D Smits}{psmits@berkeley.edu}

@@

\section*{Conclusions}

@@

\bibliography{new_bib}
